\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-15 report/paper.tex
changed to one liner sentences and squashed some equations

    Another incompressible SPH method was proposed by Hu et al.~\cite{hu} for multiphase flows where the time integration step to obtain velocities is divided into two half steps.
    This is done to enforce both zero density variaton condition and the velocity divergence-free condition at each full time step.
    During the first half step density fluctuations are eliminated by altering the intermediate particle position.
    During the second half step errors in velocity divergence are resolved by altering the intermediate particle velocity.

@@

\begin{equation}\label{eq:cfl}
\Delta t \leq \frac{0.4 \cdot d}{\vect{V_{max}}}
\end{equation}

@@

    \begin{equation}\label{eq:density}
        \rho_i = \sum_j \frac{m_j}{\rho_j} \rho_j W_{ij} = \sum_j m_j W_{ij}
    \end{equation}

@@

    \begin{equation}\label{eq:kappa}
        \kappa_i^v = \frac{1}{\Delta t} \frac{D\rho_i}{Dt} \cdot \alpha_i
    \end{equation}

@@

    \begin{equation}\label{eq:alpha}
        \alpha_i = \frac{\rho_i}{\left | \sum_j m_j \nabla \vect{W}_{ij}  \right |^2 + \sum_j \left | m_j \nabla \vect{W}_{ij} \right |^2}
    \end{equation}

@@

    \begin{equation} \label{eq:predDensity}
        \resizebox{0.88\linewidth}{!}{$
        \begin{matrix}
        \rho_i^* = \rho_i + \Delta t \frac{D\rho_i}{Dt} \\ 
        \\
        \Leftrightarrow \\ 
        \\
        \rho_i^* = \rho_i + \Delta t + \sum_j m_j 
        (\textbf{v}_i^* - \textbf{v}_j^*) \nabla \vect{W}_{ij}
        \end{matrix}
        $}
    \end{equation}

@@

    Furter on, the pressure forces $\vect{F_{j\leftarrow i}^p} $ that act from particle $i$ on all its neighbours $j$ is calculated through

@@

    \begin{equation} \label{eq:pressureTotal}
        \resizebox{0.88\linewidth}{!}{$
        \begin{matrix}
            \vect{F_{i,total}^p} = \vect{F_i^p} + \sum_j \vect{F_{i\leftarrow j}^p} \\
            \\
            \Leftrightarrow \\ 
            \\
            \vect{F_{i,total}^p} = -m_i \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W}_{ij}
        \end{matrix}
        $}
    \end{equation}

@@

    \begin{equation} \label{eq:velocity}
        \vect{v_i^*}(t) = \vect{v_i^*}(t) - \Delta t \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W}_{ij}
    \end{equation}

@@

\begin{eqnarray}
\label{eqn:quadricmatrixform}
\mathbf{p}^T\mathbf{Q}\mathbf{p} =  \left[ \begin{array}{cccc} x & y & z & 1 \end{array} \right] \left[ \begin{array}{cccc}
A & B & C &D\\
B & E & F & G\\
C & F & H & I\\
D & G & I & J\\
 \end{array} \right] \left[ \begin{array}{c}x \\
y \\
z \\
1 \end{array} \right]
\end{eqnarray}

@@

    The simulation was developed on Mac OS and Linux.
    The Linux computer is running on Debian and has four Intel(R) Core(TM) i5-2450M CPU @ 2.50GHz, one NVIDIA GeForce 610M graphics card and 6.0 GiB RAM. One of the Mac OS computer is running on macOS Sierra and has a 1.8 GHz Intel Core i5 processor with an Intel HD Graphics 400 1536 MB graphics card.

>>>>

    Another incompressible SPH method was proposed by Hu et al.~\cite{hu} for multiphase flows where the time integration step to obtain velocities is divided into two half steps.
    This is done to enforce both zero density variation condition and the velocity divergence-free condition at each full time step.
    During the first half step density fluctuations are eliminated by altering the intermediate particle position.
    During the second half step errors in velocity divergence are resolved by altering the intermediate particle velocity.

@@

\begin{equation} \label{eq:cfl}
\Delta t \leq \frac{0.4 \cdot d}{\vect{V_{max}}}
\end{equation}

@@

    \begin{equation} \label{eq:density}
        \rho_i = \sum_j \frac{m_j}{\rho_j} \rho_j W_{ij} = \sum_j m_j W_{ij}
    \end{equation}

@@

    \begin{equation} \label{eq:kappa}
        \kappa_i^v = \frac{1}{\Delta t} \frac{D\rho_i}{Dt} \cdot \alpha_i
    \end{equation}

@@

    \begin{equation} \label{eq:alpha}
        \alpha_i = \frac{\rho_i}{\left | \sum_j m_j \nabla \vect{W}_{ij}  \right |^2 + \sum_j \left | m_j \nabla \vect{W}_{ij} \right |^2}
    \end{equation}

@@

    \begin{equation} \label{eq:predDensity}
        \resizebox{0.85\linewidth}{!}{$
        \begin{matrix}
        \rho_i^* = \rho_i + \Delta t \frac{D\rho_i}{Dt} \\ 
        \\
        \Leftrightarrow \\ 
        \\
        \rho_i^* = \rho_i + \Delta t + \sum_j m_j 
        (\textbf{v}_i^* - \textbf{v}_j^*) \nabla \vect{W}_{ij}
        \end{matrix}
        $}
    \end{equation}

@@

    Further on, the pressure forces $\vect{F_{j\leftarrow i}^p} $ that act from particle $i$ on all its neighbours $j$ is calculated through

@@

    \begin{equation} \label{eq:pressureTotal}
        \resizebox{0.85\linewidth}{!}{$
        \begin{matrix}
            \vect{F_{i,total}^p} = \vect{F_i^p} + \sum_j \vect{F_{i\leftarrow j}^p} \\
            \\
            \Leftrightarrow \\ 
            \\
            \vect{F_{i,total}^p} = -m_i \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W}_{ij}
        \end{matrix}
        $}
    \end{equation}

@@

    \begin{equation} \label{eq:velocity}
        \resizebox{0.85\linewidth}{!}{$
        \vect{v_i^*}(t) = \vect{v_i^*}(t) - \Delta t \sum_j m_j (\frac{\kappa_i^v}{\rho_i} + \frac{\kappa_j^v}{\rho_i}) \nabla \vect{W}_{ij}
        $}
    \end{equation}

@@

\begin{eqnarray} \label{eqn:quadricmatrixform}
\resizebox{0.9\linewidth}{!}{$
\mathbf{p}^T\mathbf{Q}\mathbf{p} =  \left[ \begin{array}{cccc} x & y & z & 1 \end{array} \right] \left[ \begin{array}{cccc}
A & B & C &D\\
B & E & F & G\\
C & F & H & I\\
D & G & I & J\\
 \end{array} \right] \left[ \begin{array}{c}x \\
y \\
z \\
1 \end{array} \right]
$}
\end{eqnarray}

@@

    The simulation was developed on macOS and Linux.
    The Linux computer is running on Debian and has four Intel(R) Core(TM) i5-2450M CPU @ 2.50GHz, one NVIDIA GeForce 610M graphics card and 6.0 GiB RAM.
    One of the Mac OS computer is running on macOS Sierra and has a 1.8 GHz Intel Core i5 processor with an Intel HD Graphics 400 1536 MB graphics card.
